% Created 2016-02-08 月 21:44
\documentclass[a4j,12pt,oneside,openany,english]{jsbook}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{book2report}
\usepackage{thesis}

\usepackage{amssymb}
\usepackage{multirow}
\usepackage{threeparttable}
\usepackage{array}
\usepackage{color}

\usepackage{lscape}

\usepackage{nidanfloat}
\usepackage{setspace}

% \newcommand{\comment}[1]{\colorbox{green}{#1}}
\newcommand{\comment}[1]{}    


\setcounter{topnumber}{5}%    ページ上部の図表は 5 個まで
\def\topfraction{1.00}%       ページの上 1.00 まで図表で占めて可
\setcounter{bottomnumber}{5}% ページ下部の図表は 5 個まで
\def\bottomfraction{1.00}%    ページの下 1.00 まで図表で占めて可
\setcounter{totalnumber}{10}% ページあたりの図表は 10 個まで
\def\textfraction{0.00}%      ページうち本文が占める割合の下限
  

\date{\today}
\begin{document}

% 英語で，見出しのフォントが気に入らなかったら
\renewcommand{\headfont}{\bfseries}

% ページ数が少ないときはここを大きくしてごまかそう！！効果絶大！！
\renewcommand{\baselinestretch}{1.1}

%%%%%%%%%%%% 題目 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% ここも適当に変えてもいいと思う %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty}
\begin{center}
  \vspace*{5mm}
  {\Huge {\bf Master's Thesis}}\\
  \vspace{2cm}
  \vspace{1cm}
  \underline{\LARGE{Scalable Parallel Computing}} \\
  \vspace{0.2cm}  
  \underline{\LARGE{on NoC-based Embedded Many-Core Platform}} \\  
  \vspace{0.5cm}
  \vspace{12mm}
  {\large Supervisor}\\
  \vspace{6mm}
  \underline{\Large Professor Toshimitsu Ushio}\\
  　\\
  \underline{\Large Assistant Professor Takuya Azumi}\\
  \vspace{8mm}
  {\large By}\\
  \vspace{6mm}
  \underline{\Large Yuya Maruyama}\\
  \vspace{10mm}
  {\Large February xx, 2018}\\  
  \vspace{14mm}
  {\Large Division of Mathmatical Science for Social System,\\
    Department of Systems Innovation,\\
    Graduate School of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}

%%%%%%%%%%%% 概要 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This paper presents evaluations of parallel computing on embedded many-core platforms.
  In embedded systems, high processing requirements and low power consumption require heterogeneous computing platforms including many-core platforms.
  Considering nonuniform memory access (NUMA) for scalability, many-core applications must be designed based on scalable data allocation and scalable parallel computing.
  As a reference embedded many-core computing platform, we use the Massively Parallel Processor Arrays 256 (MPPA-256) developed by Kalray, one of the commercial off-the-shelf (COTS) multi-/many-core platforms.
  In this paper, we conduct evaluations of data transfer on network-on-chip (NoC) implementations, microbenchmarks, and parallelization of a practical application on NoC-based embedded many-core platforms.
  We investigate currently achievable data transfer latencies between distributed memories on NoC systems, memory access characteristics with NUMA, and parallelization scalability of many cores.
  As a practical application, we parallelize a portion of the self-driving algorithms on many-core processors.
  We believe that this performance level is acceptable for the real-world production of autonomous vehicles.
  By highlighting many-core computing capabilities, we explore scalable parallel computing on NoC-based embedded many-core platforms.
\end{abstract}

%%%%%%%%%%%% 目次 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\tableofcontents
\clearpage
\setcounter{page}{0}
\pagenumbering{arabic}

%%%%%%%%%%%%% ここから内容 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{thesis_master_body}

%%%%%%%%%%%% Apendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter*{Apendix A: Robot Operating System (ROS)}
\addcontentsline{toc}{chapter}{Apendix A: Robot Operating System (ROS)}
\setcounter{chapter}{1}
\label{sec:ros}

\input{thesis_master_apendixA}

\chapter*{Apendix B: Autoware}
\addcontentsline{toc}{chapter}{Apendix B: Autoware}
\setcounter{chapter}{1}
\label{sec:autoware}

\input{thesis_master_apendixB}


%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{acknowledgement}
  This paper was partly supported by Toyota Motor Company, eSOL, and Kalray.
  In addition, this research was partially supported by JST, PRESTO.
\end{acknowledgement}


%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{IEEEtran}
\bibliography{./reference.bib}


%%%%%%%%%%%% Publication List %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Publication List}
\addcontentsline{toc}{chapter}{Publication List}

% \section*{International Conference Proceedings}
% \renewcommand{\labelenumi}{[\arabic{enumi}]}
% \begin{enumerate}
% \item Y.Maruyama, S.Kato, and T.Azumi,
%   ``{Impact of DDS on ROS2},''
%   \emph{In Proceedings of the 19th IEEE International Symposium on Real-Time Computing (ISORC2016)}, 2016.
%   (submitted)
% \item Y.Maruyama, S.Kato, and T.Azumi,
%   ``{Preliminary Evaluation of ROS2},''
%   \emph{WiP session of the ACM/IEEE 7th International Conference on Cyber-Physical Systems (ICCPS2016)}, 2016.
%   (accepted)
% \end{enumerate}

\end{document}

